Paper template for {ICPhS} 2023 Prague

### 2024-04-25 manuscript/main.Rmd
update

>>>>

\section{Methods}

\subsection{Materials}

Data were collected using an online survey hosted on Qualtrics that consisted of two parts. The first part, a demographic questionnaire, collected information regarding participant age, gender, place of origin, place of residence, mother tongue, family income, and level of studies. The second portion of the survey consisted of a perception task where participants were presented with a series of stimuli containing the target phoneme contrast (intervocalic voiced and voiceless alveolar fricative) followed by 11 evaluative statements related to social characteristics such as level of studies, friendliness, social class, and ethnic origin. These evaluative statements were then followed by a 100-point draggable sliding scale with which participants indicated their level of agreement or disagreement with the content of the statement, where 0 was “totally disagree” and 100 was “totally agree”.

The target stimuli were recorded by a 28-year-old female native speaker of Catalan in a whisper room 6084 E sound booth using a personal communication device. The stimuli were between 3 and 4 seconds long and were controlled for utterance length (5 words), syllable count (2 syllables for the target word and 3 for the following adjective), and lexical stress (target sound in unstressed position). A total of 12 target stimuli containing intervocalic voiced /s/ were recorded, as well as different samples of the voiceless /s/. The target sentences were manipulated in Praat by splicing the voiced /s/ and pasting the voiceless /s/ in order to create 2 conditions: 12 stimuli containing intervocalic voiced /s/ and 12 stimuli containing intervocalic voiceless /s/, for a total of 24 experimental sentences. These sentences were combined with 32 fillers targeting other phonemic contrasts, for a total of 56 sentences randomly distributed in two different versions. Each included 12 experimental stimuli (6 x 2 conditions) and 16 fillers (8 x 2 conditions).

\subsection{Procedure}

Participants self-identified for this study. Recruitment materials in Catalan with information about the study, the requirements to participate and a link to the survey were posted on different social networks and online communication channels, such as WhatsApp and Instagram. Participants who were interested and wanted to participate clicked on the link and read the study description. Those who decided to participate completed the survey on their own electronic devices and at their own pace without being observed. On average, the survey took approximately 15 minutes to be completed. The survey followed a between-subjects design. Therefore, participants were randomly assigned to one of the two versions.

\subsection{Participants}

A total of 78 responses to the questionnaire were collected. Of these, 56 responses were incomplete and were therefore discarded. Data are drawn from a total of 22 participants (13 females) aged between 18 and 72 years old (mean = 38) from Barcelona and Girona. In order to be eligible to take part in the study, participants had to meet the following three requirements: to be over 18 years of age, to be from Catalonia, and to be proficient in both Catalan and Spanish.

\subsection{Data analysis}

Data were analyzed in R (R Core Team, 2023). First, we performed a descriptive analysis that consisted of creating a series of plots and tables to summarize and describe the features of the dataset and to identify potential trends. After that, we performed inferential statistical analysis. For each of the 11 evaluative statements, we created a series of hierarchically nested linear regression models using the lme4 package (Bates et al., 2015) with attitudinal sliding scale responses as the dependent variable, and phoneme, mother tongue, and province as potential predictors. To determine the best fit model for each statement, we used the anova() function (Fox & Weisberg, 2019).
